Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher

### 2016-03-31 pets2017-paper/pets2017-paper.tex
deleted extra period.
added subsections
added flow figures

\section{Background} 
\subsection{The Interface} 
{\color {red} storyboard of the old interface

\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
    \item No bridge, no proxy
    \item with bridge, no proxy
    \item No bridge, with proxy
    \item With bridge, with proxy
\end{enumerate}
}
\subsection{Kinds of Users} 
\subsection{Network Components} 
\subsection{Censorship Environments}

@@

\section{Qualitative Analysis of the Existing Interface (Study 1)}
We performed qualitative research as an exploratory effort to gain an 
understanding of underlying problems, such as reasons for confusion 
during the configuration process and motivations for particular choices in 
configuration. We did this through observing each participant as they 
interacted with Tor Browser 5.0.3. interface and interviewed them about
their experience. This study provides insights into particular problems with 
the current Tor Browser configuration interface, and helps us to design
a new interface which addresses these problems and gives foundation
for hypotheses to test in quantitative research.

@@

>>>>

\section{Background}

\subsection{The Interface}

\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{old-flow.pdf} 
		\caption{old flow} 
\end{figure*}

{\color {red} storyboard of the old interface

\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
    \item No bridge, no proxy
    \item with bridge, no proxy
    \item No bridge, with proxy
    \item With bridge, with proxy
\end{enumerate}
}

\subsection{Kinds of Users}

\subsection{Network Components}

\subsection{Censorship Environments}

@@

\section{Qualitative Analysis of the Existing Interface (Study 1)}
We performed qualitative research as an exploratory effort to gain an 
understanding of underlying problems, such as reasons for confusion 
during the configuration process and motivations for particular choices in 
configuration. We did this through observing each participant as they 
interacted with Tor Browser 5.0.3 interface and interviewed them about
their experience. This study provides insights into particular problems with 
the current Tor Browser configuration interface, and helps us to design
a new interface which addresses these problems and gives foundation
for hypotheses to test in quantitative research.

@@

\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
		\caption{new flow} 
\end{figure*}
